\documentclass[12pt]{article}
\usepackage[charter]{mathdesign}
\usepackage{microtype}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[a4paper,margin=1in,heightrounded]{geometry}
\title{Compere}
\author{Kalaivani}
%
\begin{document}
  \maketitle
  \doublespacing
  \begin{enumerate}
    \item A pleasant morning to one and all gathered here.  I feel greatly honored in welcoming the reputed personalities and the gatherings for the AICTE QIP sponsored one week short term course on \emph{ICT Solutions for Issues and Challenges in Smart Grid Technology} on behalf of Department of Electrical \& Electronics Engineering and Department of Information Technology.
    \item Let us start this flamboyant occasion with the blessings of God the almighty. I request all to raise for the invocation.
    \item May I now request the coordinator Dr.\, V. Geetha to deliver the formal welcome address.
    \item Light vanishes the darkness of life. Lightning ensures the brightness and happiness of life. So, I invite our dignitaries to enlighten the kuthuvilaku.
    \item Felicitating the chief guest gives more pleasure and it is sign of expressing our honor towards the guest which is our tradition. So I request \underline{\hspace{1.5in}} to felicitate our chief guest Prof.\,\underline{\hspace{1.5in}}
    \item Now I request the coordinator of Course Dr.\,R. Rajathy to give an outline about the course.
    \item Our Chief guest Prof.\,\underline{\hspace{1.5in}} is a man of hardwork and sincerity. Now comes the chief guest address which is the long awaited moment of this hour. Yes friends, now we all can have some food for our thought.
    \item Let's all disperse for the photo session in front of the library.
  \end{enumerate}

\end{document} 